Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
more \ref fix.

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section~\ref{ref:Best-current-practice})

@@

%%%%%%%%%%%%%%%%
\subsubsection{Expecting exceptions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practices}
\label{ref:Best-current-practice}

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow} described in Section~\ref{todo}.

>>>>

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section~\ref{sec:best-current-practice})

@@

%%%%%%%%%%%%%%%%
\subsubsection{Expecting exceptions}
\label{sec:expacting-exceptions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practices}
\label{sec:best-current-practice}

@@

The {\tt testpack} package provides a function to check
exception, similar to {\tt shouldThrow} described in Section~\ref{sec:expacting-exceptions}.
